Testing and Isolation Efficacy; Insights from a Simple Epidemic Model

### 2020-12-04 SIR_manuscript.tex
more edits on Intro section

\jd{This \P\ is confusing. The topic sentence seems to be about kinds of tests, and then there is a jump to sampling strategies.}
There are different testing strategies with different test-specific efficacy, the time required for the results to be reported and the cost of the test. Testing strategies can be grouped into two categories including (i) random testing across the whole population and (ii) Non-random testing. \jd{Random testing is not a broad category, and non-random testing is very vague. What are we trying to convey with this \P?} \ali{I am thinking of the weighted testing parameters W's in our model, that reflects testing strategies.(not sure the best replacement for "non-random" testing?)} Note that contact tracing is an example of non-random testing strategies. Each of these strategies has been used as a tool to study COVID-19; see (refs) for group (i) and (refs) for group (ii). The advantage of non-random testing comparing to random testing has been investigated specifically during the COVID-19 pandemic (refs).

There is useful comment from Troy Gayle [?, Ben?] on the purposes of testing:"The importance of the relative roles of at least four different, and sometimes conflicting, purposes of testing: (i) diagnosis and treatment, (ii) screening people for access to things like flights, surgery, LTCs etc, (iii) surveillance, and (iv) mitigation and control of disease spread." In this context, the random testing, the simplest form of testing strategy, is typically carried out for the purpose of surveillance. It is notable that, by random testing we mainly refer to PCR test given that there is almost negligable virological testing for survilance purposes. Furthermore, all of the accessible testing data is being used for one of the other three purposes rather than surveillance. These are non-random testing strategies with a different bios. Specifically, when the purpose is "(i) diagnosis and treatment" or "(iv) mitigation and control of disease spread", the bios is towards infectious individuals more strongly for (i) than (iv). When people are tested for "(ii) screening", the bios is towards the group-specific charactristics [I am making this up for now!]. For example, people who are getting on flights may/will be more mobile than people awaiting for a surgery and are probably going to stay in long-term care homes and consequently more isolated to begin with.

Much effort has been invested in developing widely accessible and fast tests in order to mitigate the spread of the pandemic (refs). For example, PCR tests are commonly used, and very sensitive, but take longer compared to more recent tests, such as a breath-based test currently in trial stage, which can provide a result in seconds.

>>>>

\jd{This \P\ is confusing. The topic sentence seems to be about kinds of tests, and then there is a jump to sampling strategies.}

It is often the purpose of testing, apart from the testing infrastructure, that dictates/defines \ali{[better word?]} the testing strategy. There are at least four different, and sometimes conflicting, purposes of testing: (i) diagnosis and treatment, (ii) screening people for access to things like flights, surgery, LTCs etc, (iii) surveillance, and (iv) mitigation and control of disease spread (ref to Troy Gayle?). Further, the testing strategies can be grouped into two categories including random testing across the whole population and Non-random/biosed testing. Random testing is the simplest form of testing strategy and is typically carried out for the purpose of surveillance. It is notable that, by random testing we mainly refer to PCR test given that there is almost negligable virological testing for survilance purposes. Furthermore, all of the accessible testing data is being used for one of the other three purposes rather than surveillance. These are non-random testing strategies with a different bios. Specifically, when the purpose is "(i) diagnosis and treatment" or "(iv) mitigation and control of disease spread", the bios is towards infectious individuals more strongly for (i) than (iv). When people are tested for "(ii) screening", the bios is towards the group-specific charactristics [I am making this up for now!]. For example, people who are getting on flights may/will be more mobile than people awaiting for a surgery and are probably going to stay in long-term care homes and consequently more isolated to begin with.

-Examples of random versus biosed testing strategies;
Each of these strategies has been used as a tool to study COVID-19; see (refs) for group (i) and (refs) for group (ii). The advantage of non-random testing comparing to random testing has been investigated specifically during the COVID-19 pandemic (refs).

- Speed of test; 
Much effort has been invested in developing widely accessible and fast tests in order to mitigate the spread of the pandemic (refs). For example, PCR tests are commonly used, and very sensitive, but take longer compared to more recent tests, such as a breath-based test currently in trial stage, which can provide a result in seconds.
